Generating the Blueprints of the Java Ecosystem

### 2015-02-28 msr.tex
minor fix
removed headers from tables
several minor fixes

\begin{table}
\centering
\caption{Class Design Metrics}
\label{tbl:class-selected-metrics}
\begin{tabular}{l l}
 \hline
\multicolumn{2}{l}{\textit{\textbf{Class Design}}}\\
\hline
Depth Of Inheritance Tree & \textit{ckjm}\\
Coupling Between Objects & \textit{ckjm}\\
Weighted Methods Per Class & \textit{ckjm}\\
Response For Class & \textit{ckjm}\\
Lack Of Cohesion In Methods & \textit{ckjm}\\
Number Of Children & \textit{ckjm}\\
Attribute Hiding Factor & \textit{clmt}\\
Coupling Between Methods & \textit{ckjm}\\
Average Method Complexity & \textit{ckjm}\\
Cohesion Among Methods of Class & \textit{ckjm}\\
Data Access Metric & \textit{ckjm, clmt}\\
Inheritance Coupling & \textit{ckjm}\\
Lack Of Cohesion In Methods3 & \textit{ckjm}\\
Measure Of Aggregation & \textit{ckjm}\\
Measure Of Functional Abstraction & \textit{ckjm}\\
Number of Attributes & \textit{clmt}\\
Method Hiding Factor & \textit{clmt}\\
\hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Method Design Metrics}
\label{tbl:method-selected-metrics}
\begin{tabular}{l l}
 \hline
\multicolumn{2}{l}{\textit{\textbf{Method Design}}}\\
\hline
Number of Method Parameters & \textit{clmt}\\
Number of Methods & \textit{clmt, ckjm}\\
McCabe Cyclomatic Complexity & \textit{ckjm, clmt}\\
\hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Package Design Metrics}
\label{tbl:package-selected-metrics}
\begin{tabular}{l l}
 \hline
\multicolumn{2}{l}{\textit{\textbf{Package Design}}}\\
\hline
Number of Concrete Classes & \textit{jdep}\\
Afferent Couplings & \textit{jdep, ckjm}\\
Efferent Couplings & \textit{jdep, ckjm}\\
Instability & \textit{jdep}\\
Abstractness & \textit{jdep}\\
Distance Main Sequence & \textit{jdep}\\
\hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Program Size Metrics}
\label{tbl:size-selected-metrics}
\begin{tabular}{l l}
 \hline
\multicolumn{2}{l}{\textit{\textbf{Program Size Metrics}}}\\
\hline
Number of Classes & \textit{clmt, ckjm, jdep}\\
Number of Enumerations & \textit{clmt, ckjm}\\
Number of Interfaces & \textit{clmt, ckjm}\\
Module Count & \textit{clmt, ckjm}\\
Comments Lines Of Code & \textit{clmt}\\
Lines Of Code & \textit{clmt, ckjm}\\
Source Lines Of Code & \textit{clmt}\\
Function Oriented Code & \textit{clmt}\\
DSL Usage Count & \textit{clmt}\\
RTF Usage Count & \textit{clmt}\\
Regex Usage Count & \textit{clmt}\\
HTML Usage Count & \textit{clmt}\\
XPath Usage Count & \textit{clmt}\\
XSLT Usage Count & \textit{clmt}\\
XML Usage Count & \textit{clmt}\\
SQL Usage Count & \textit{clmt}\\
File Count & \textit{clmt}\\
\hline
\end{tabular}
\end{table}

@@

The measurements provided by our dataset, can be used by researchers and practitioners alike. Researchers can use the data to experiment with new quality models, or validate them in real projects. Practitioners who develop tools that calculate metrics can use the dataset to validate if their tools work correctly.

@@

\begin{table}
\centering
\caption{DSL Usage Combinations Ranking}
\label{tbl:dsl-top-usage}
\begin{tabular}{l r}
 \hline
\textbf{DSLs} & \textbf{Count}\\
\hline
XML & 1,561\\
Regex & 909\\
SQL & 493\\
XML, XSLT & 475\\
Regex, XML, XSLT & 158\\
Regex, XML & 303\\
SQL, XML & 162\\
Regex, SQL & 116\\
Regex, SQL, XML, XSLT & 80\\
Regex, SQL, XML & 71\\
SQL, XML, XSLT & 54\\
XML, XPath & 50\\
\hline
\end{tabular}
\end{table}

The initial goal of this experiment was to provide quantifiable results that are indicative regarding the usage of {\sc dsl}s in multiple Java projects. The related metrics can be found in the database table named \textit{measuremnt\_type}, and they are the following: \textit{RTFUsage\_clmt}, \textit{RegexUsage\_clmt},
\textit{HTMLUsage\_clmt}, \textit{HTMLUsage\_clmt}, \textit{XPathUsage\_clmt}, \textit{XSLTUsage\_clmt}, \textit{XMLUsage\_clmt}, \textit{SQLUsage\_clmt}, and \textit{DSLCount\_clmt}. With a python script that analyses the measurements stored in the database, we produced Table~\ref{tbl:dsl-top-usage}. This table, lists popular {\sc dsl} usage combinations found in our dataset. An interesting observation is that {\sc xml} is the most widespread {\sc dsl} with 1561 occurrences in 11365 projects (13\%). Regular expressions are also popular with 909 occurrences (7\%). Note that the numbers represents the projects where {\sc xml} and regular expressions were used as the only {\sc dsl}.

>>>>

\begin{table}
\centering
\caption{Class Design Metrics}
\label{tbl:class-selected-metrics}
\begin{tabular}{l l}
\hline
Depth Of Inheritance Tree & \textit{ckjm}\\
Coupling Between Objects & \textit{ckjm}\\
Weighted Methods Per Class & \textit{ckjm}\\
Response For Class & \textit{ckjm}\\
Lack Of Cohesion In Methods & \textit{ckjm}\\
Number Of Children & \textit{ckjm}\\
Attribute Hiding Factor & \textit{clmt}\\
Coupling Between Methods & \textit{ckjm}\\
Average Method Complexity & \textit{ckjm}\\
Cohesion Among Methods of Class & \textit{ckjm}\\
Data Access Metric & \textit{ckjm, clmt}\\
Inheritance Coupling & \textit{ckjm}\\
Lack Of Cohesion In Methods3 & \textit{ckjm}\\
Measure Of Aggregation & \textit{ckjm}\\
Measure Of Functional Abstraction & \textit{ckjm}\\
Number of Attributes & \textit{clmt}\\
Method Hiding Factor & \textit{clmt}\\
\hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Method Design Metrics}
\label{tbl:method-selected-metrics}
\begin{tabular}{l l}
\hline
Number of Method Parameters & \textit{clmt}\\
Number of Methods & \textit{clmt, ckjm}\\
McCabe Cyclomatic Complexity & \textit{ckjm, clmt}\\
\hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Package Design Metrics}
\label{tbl:package-selected-metrics}
\begin{tabular}{l l}
\hline
Number of Concrete Classes & \textit{jdep}\\
Afferent Couplings & \textit{jdep, ckjm}\\
Efferent Couplings & \textit{jdep, ckjm}\\
Instability & \textit{jdep}\\
Abstractness & \textit{jdep}\\
Distance Main Sequence & \textit{jdep}\\
\hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Program Size Metrics}
\label{tbl:size-selected-metrics}
\begin{tabular}{l l}
 \hline
Number of Classes & \textit{clmt, ckjm, jdep}\\
Number of Enumerations & \textit{clmt, ckjm}\\
Number of Interfaces & \textit{clmt, ckjm}\\
Module Count & \textit{clmt, ckjm}\\
Comments Lines Of Code & \textit{clmt}\\
Lines Of Code & \textit{clmt, ckjm}\\
Source Lines Of Code & \textit{clmt}\\
Function Oriented Code & \textit{clmt}\\
DSL Usage Count & \textit{clmt}\\
RTF Usage Count & \textit{clmt}\\
Regex Usage Count & \textit{clmt}\\
HTML Usage Count & \textit{clmt}\\
XPath Usage Count & \textit{clmt}\\
XSLT Usage Count & \textit{clmt}\\
XML Usage Count & \textit{clmt}\\
SQL Usage Count & \textit{clmt}\\
File Count & \textit{clmt}\\
\hline
\end{tabular}
\end{table}

@@

The measurements provided by our dataset, can be used by researchers and practitioners alike. Researchers can use the data to experiment with new software quality models, or validate them with real projects. Practitioners who develop tools that calculate metrics can use the dataset to validate if their tools produce correct results.

@@

\begin{table}
\centering
\caption{Top DSL Usage Combinations}
\label{tbl:dsl-top-usage}
\begin{tabular}{l r}
 \hline
\textbf{DSLs} & \textbf{Count}\\
\hline
XML & 1,561\\
Regex & 909\\
SQL & 493\\
XML, XSLT & 475\\
Regex, XML, XSLT & 158\\
Regex, XML & 303\\
SQL, XML & 162\\
Regex, SQL & 116\\
Regex, SQL, XML, XSLT & 80\\
Regex, SQL, XML & 71\\
SQL, XML, XSLT & 54\\
XML, XPath & 50\\
\hline
\end{tabular}
\end{table}

The initial goal of this experiment was to provide quantifiable results that are indicative regarding the usage of {\sc dsl}s in multiple Java projects. The related metrics can be found in the database table named \textit{measuremnt\_type}, and they are the following: \textit{RTFUsage}, \textit{RegexUsage}, \textit{HTMLUsage}, \textit{HTMLUsage}, \textit{XPathUsage}, \textit{XSLTUsage}, \textit{XMLUsage}, \textit{SQLUsage}, and \textit{DSLCount}. A Python script that analysed the measurements stored in the database, we produced the results illustrated in Table~\ref{tbl:dsl-top-usage}. This table, lists popular {\sc dsl} usage combinations found in our dataset. An interesting observation is that {\sc xml} is the most widespread {\sc dsl} with 1,561 occurrences in 11,365 projects (13\%). Regular expressions are also popular with 909 occurrences (7\%). Note that the numbers represents the projects where {\sc xml} and regular expressions were used as the only {\sc dsl}.
